Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-03-23 paper/ms.tex
Add discussion of gas corotation

>>>>

{\bf We also note that since \citet{2011MNRAS.415.1027H} predicts gas outside of
corotation will flow outward, the bar should exert a positive torque on that
gas. Indeed, we measured the average torque on gas outside corotation from
$t=3\,\textrm{Gyr}$ to $5\,\textrm{Gyr}$ to be $0.87$ in code units
($10^{10}\,M_{\odot}\,(\text{km}/\text{s})^2$). For reference, the average
torque inside corotation is $-10.8$ over the same time period and in the same
units. So, while gas outside corotation does experience a positive torque, the
total torque on the gas phase is still negative.}
